Identifying and correcting for misspecifications\\in GWAS summary statistics for polygenic scores

### 2022-02-04 paper/paper-misspec-supp.tex
update intro

@@

>>>>

\begin{figure}[p]
	\centerline{\includegraphics[width=0.98\textwidth]{compare-all-maf-info-chr22}}
	\caption{Minor allele frequencies (MAF) and INFO scores in the UK Biobank for 50,000 variants on chromosome 22 (chosen at random). These are either reported (in UKBB MFI files), recomputed from the whole data or from the subset of 362,307 European individuals used in this paper. \label{fig:compare-maf-info}}
\end{figure}

@@

\begin{figure}[h]
	\centerline{\includegraphics[width=0.95\textwidth]{simu-rounded}}
	\caption{Results for the simulations with summary statistics (effect sizes and their standard errors) possibly rounded to two significant digits, averaged over 10 simulations for each scenario. Reported 95\% confidence intervals are computed from 10,000 non-parametric bootstrap replicates of the mean. Red bars correspond to using the LD with independent blocks (Methods).}
	\label{fig:simu-rounded}
\end{figure}
